### 2023-08-11 chapters/background.tex
Minor revisions

To the general public, the concept of uncertainty goes by many names, and its meaning can vary depending on the specific context. However, across most quantitative scientific fields, a consensus definition appears to align with the following \cite{hubbard_how_2014}:

@@

While a purely lexical definition of uncertainty might trigger a philosophical inquisition, information theory provides a mathematically rigorous method for quantifying uncertainty through the language of probabilities. 
In this context, uncertainty is understood as the information entropy of a random variable \cite{mackay_information_2003}.

>>>>

In society, the concept of uncertainty goes by many names, and its meaning can vary depending on the specific context. However, across most quantitative scientific fields, a consensus definition appears to align with the following \cite{hubbard_how_2014}:

@@

While such a purely lexical definition of uncertainty might trigger a philosophical inquisition, information theory provides a mathematically rigorous method for quantifying uncertainty through the language of probabilities. 
In this context, uncertainty is understood as the information entropy of a random variable \cite{mackay_information_2003}.
